Improving the communication and transparency of stock assessment using interactive

### 2018-11-21 analysis/paper/manuscript.Rmd
Re-structure files and add data and scripts required to make the NCAM dashboard

TODO:
- Copy the data and functions required to run the flexdashboard file here
- Consider taking the flexdashboard outside of the vis_fit function
- Fix up the projection bits of the code in the Rmd file
- Take screenshots of the dashboard for static figures for the paper
- Produce the html file for this paper and include refrence to supplment

>>>>

TODO:
- Take screenshots of the dashboard for static figures for the paper (use webshot?)
- Remember to add reference to the supplement that will ultimatly include the NCAM_dashboard.html
